\SetAPI{J-C}
\section{IJobExtendable}
\label{extendable:IJobExtendable}
\ClearAPI

The \javadoc{com.koch.ambeth.job.IJobExtendable}{IJobExtendable} extendable is responsible for register and unregister cron jobs for the \prettyref{module:Job} API.
\javadoc{com.koch.ambeth.job.IJob}{IJob} is the extension to the \type{IJobExtendable} extendable. 
The registration of a \type{IJob} requires two parameters.
\begin{enumerate}
	\item jobName: used for the backed scheduling framework, unique identification and debugging purposes. (the jobNames must be unique)
	\item cronPattern: a UNIX crontab-like pattern to schedule the job repetition.
\end{enumerate}
The JavaDoc on the \javadoc{com.koch.ambeth.job.IJob}{IJob} interface describes possible detailed configurations for a job e.g. pause support or status support.
For detailed instructions on how to use the pattern please refer to \href{http://www.sauronsoftware.it/projects/cron4j/manual.php#p02}{cron4j documentation.}
A small introduction on cron patterns. There are five positions (* * * * *). A star * is for ``every'' (e.g. every minute). The positions:
\begin{enumerate}
	\item Minutes
	\item Hours
	\item Days of month
	\item Month
	\item Days of week
\end{enumerate}
Examples (see the cron4j documentation for more)
\begin{itemize}
	\item * * * * * : every minute
	\item 5 * * * * : every hour plus 5 minutes (00:05, 01:05 ...)
	\item 10,20 * * * * : on 10 minutes and 20 minutes of an hour (00:10, 00:20, 01:10, 02:20...)
	\item */5 * * * *: every 5 minutes
	\item 1-3 * * * * : starting with minute 1 of an hour, every minute to minute 3 of an hour ( 00:01, 00:02, 00:03,...)
	\item 0-15/5 * * * * : every 5 minutes from the minute 0 to the minute 15 of an hour (00:00, 00:05, 00:10, 00:15, 01:00, ...)
	\item 0 5 * * * | 6 10 * * *: combine pattern with a pipe (05:00 and 10:06)
\end{itemize}

%% GENERATED LISTINGS - DO NOT EDIT
\inputjava{Extension point for instances of \type{IJob}}
{jambeth-job/src/main/java/com/koch/ambeth/job/IJobExtendable.java}
\begin{lstlisting}[style=Java,caption={Example to register to the extension point (Java)}]
IBeanContextFactory bcf = ...
IBeanConfiguration myExtension = bcf.registerBean(...);
bcf.link(myExtension).to(IJobExtendable.class).with(...);
\end{lstlisting}
%% GENERATED LISTINGS END
